### 2014-08-31 fundamentals/intro.tex
improvement of the discrete objects section

\subsubsection{Discrete Resource Tracking}
% enables more realistic models and metrics
% material routing metrics
% shadow fuel cycles
% etc.

Not all simulations can be successfully run with a fleet-based model that 
doesn't distinguish between discrete materials. Shadow fuel cycles are an 
example.

A discrete resource model allows for a range of modeling granularity. In the
macroscopic extreme, it is equivalent to time-stepped continuous flow. In the
microscopic extreme, the model is capable of representing individual fuel
assemblies.

>>>>

\subsubsection{Discrete Objects}
% enables more realistic models and metrics
% material routing metrics
% shadow fuel cycles
% etc.

\Cyclus models facilities, institutions, regions, and resources as discrete 
objects. A discrete resource model allows for a range of modeling granularity. In the
macroscopic extreme, it is equivalent to time-stepped continuous flow. In the
microscopic extreme, the model is capable of representing arbitrarily small 
material objects at isotopic resolution. In this way, the \Cyclus simulator is 
applicable across the full range of modeling extremes.

This generality specifically permits the use cases that cannot be acheived with 
fleet-based models. That is, some questions require resolution at the level of 
individual facilities and individual materials.  Since fleet-based, 
lumped-material models do not distinguish between discrete facility entities or 
discrete materials, many detailed performance metrics cannot be captured with 
those tools.

One example use case seeks to capture system vulnerability to nefarious 
material diversion. This type of analysis requires discrete simulation of a 
target facility and the individual materials modified within it and is only 
acheivable with discretely-modeled objects like those in the \Cyclus simulator.
